---
title: "Initial Korean covid 19"
author: "Hyaden Wood"
date: "Spring 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020

$H_0$ men and women are more likley to die in south korea than other countries through 1 Jan to 1 May         
$H_A$ men and women arent more likley to die in south koreaa than other countries through 1 Jan to 1 May

### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?


```{r}
plot(deceased_date~Sex,data=kRdata)
```
This graph shows the number of decaesed cases in males and females. The total is very low for both but it does edge a little closer in deaths towards Males


## Graphical results - use ggplot commands to do this  

```{r}
basicCN <- ggplot(kRdata,aes(x=result,y=country))
```

```{r}
basicCN + geom_boxplot()
```
  This is a graph that shows the countries most effected by the deaths of covid 19 were mongolia and koreaa 
  
## Numerical results


## Inferential results 




## Conclusions

