---
title: "Initial Korean covid 19"
author: "Hyaden Wood"
date: "Spring 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020

$H_0$ men and women are more likley to die in south korea than other countries through 1 Jan to 1 May         
$H_A$ men and women arent more likley to die in south koreaa than other countries through 1 Jan to 1 May

### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?


```{r}
plot(deceased_date~Sex,data=kRdata)
```
This graph shows the number of decaesed cases in males and females. The total is very low for both but it does edge a little closer in deaths towards Males


## Graphical results - use ggplot commands to do this  


```{r}
basicNN <- ggplot(kRdata,aes(y=country,x=result))
```
 
  


```{r}
basicNN + geom_point()
```
   This is a graph that shows the countries most effected by the deaths of covid 19 were mongolia and koreaa
 

  
## Numerical results


```{r}
cont_table <- table(kRdata$country, kRdata$result)
```

```{r}
print(cont_table)
```
With these results it shows that korrea was heavily affected by the deaths of the covid 19 disease. To get this plot i simply made a cont_table with the different results from each country 

## Inferential results 

```{r}
chi_sq_test <- chisq.test(cont_table)
print(chi_sq_test)
```
This gives us a p value of 2e-06

## Conclusions

Based on the analysis of the contingency table and the results of the chi-square test (p < 0.05), there is strong evidence to reject the null hypothesis. This suggests that there is a significant association between the country of origin and the outcome (dead/alive) of the individuals. so we would reject the $H_0$